### 2021-10-26 documents/floats/pwaireg.tex
removed 'sleep' cognates

\begin{table}
\centering
\caption[Regular \PWai verbs]{Regular \qu{to fall} (\gl{s_a_}) and \qu{to sleep} (\gl{s_p_}) in \PWai \parencites[209, 211]{hawkins1953waiwai}[189, 190, 196]{hixkaryanaderby1985}[150]{howard2001wrought}[30]{waiwaihawkins1998}}
\label{tab:pwaireg}
\begin{tabular}[t]{@{}lllllll@{}}
\mytoprule
{} & \multicolumn{2}{l}{\PWai} & \multicolumn{2}{l}{\hixka} & \multicolumn{2}{l}{\waiwai} \\
{} &     \qu{to fall} &      \qu{to sleep} &     \qu{to fall} &   \qu{to sleep} &       \qu{to fall} &      \qu{to sleep} \\
\midrule
\gl{1}   &  \obj{k-eɸurka-} &   \obj{kɨ-wɨnɨkɨ-} &  \obj{k-ehurka-} &  \obj{kɨ-nɨkɨ-} &    \obj{k-eɸɨrka-} &   \obj{kɨ-wɨnɨkɨ-} \\
\gl{2}   &  \obj{m-eɸurka-} &    \obj{o-wɨnɨkɨ-} &  \obj{m-ehurka-} &  \obj{o-wnɨkɨ-} &    \obj{m-eɸɨrka-} &   \obj{mɨ-wɨnɨkɨ-} \\
\gl{1+2} &  \obj{t-eɸurka-} &  \obj{tɨt-wɨnɨkɨ-} &  \obj{t-ehurka-} &  \obj{tɨ-nɨkɨ-} &  \obj{t͡ʃ-eɸɨrka-} &  \obj{tɨt-wɨnɨkɨ-} \\
\gl{3}   &  \obj{ɲ-eɸurka-} &   \obj{nɨ-wɨnɨkɨ-} &  \obj{ɲ-ehurka-} &  \obj{nɨ-nɨkɨ-} &    \obj{ɲ-eɸɨrka-} &   \obj{nɨ-wɨnɨkɨ-} \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Regular \PWai verbs]{Regular \qu{to fall} (\gl{s_a_}) and \qu{to sleep} (\gl{s_p_}) in \PWai \parencites[150]{howard2001wrought}[189, 190, 196]{hixkaryanaderby1985}[209, 211]{hawkins1953waiwai}[30]{waiwaihawkins1998}}
\label{tab:pwaireg}
\begin{tabular}[t]{@{}lllllll@{}}
\mytoprule
{} & \multicolumn{2}{l}{\PWai} & \multicolumn{2}{l}{\hixka} & \multicolumn{2}{l}{\waiwai} \\
{} &     \qu{to fall} &      \qu{to sleep} &     \qu{to fall} &   \qu{to sleep} &       \qu{to fall} &      \qu{to sleep} \\
\midrule
\gl{1}   &  \obj{k-eɸurka-} &   \obj{kɨ-wɨnɨkɨ-} &  \obj{k-ehurka-} &  \obj{kɨ-nɨkɨ-} &    \obj{k-eɸɨrka-} &   \obj{kɨ-wɨnɨkɨ-} \\
\gl{2}   &  \obj{m-eɸurka-} &    \obj{o-wɨnɨkɨ-} &  \obj{m-ehurka-} &  \obj{o-wnɨkɨ-} &    \obj{m-eɸɨrka-} &   \obj{mɨ-wɨnɨkɨ-} \\
\gl{1+2} &  \obj{t-eɸurka-} &  \obj{tɨt-wɨnɨkɨ-} &  \obj{t-ehurka-} &  \obj{tɨ-nɨkɨ-} &  \obj{t͡ʃ-eɸɨrka-} &  \obj{tɨt-wɨnɨkɨ-} \\
\gl{3}   &  \obj{ɲ-eɸurka-} &   \obj{nɨ-wɨnɨkɨ-} &  \obj{ɲ-ehurka-} &  \obj{nɨ-nɨkɨ-} &    \obj{ɲ-eɸɨrka-} &   \obj{nɨ-wɨnɨkɨ-} \\
\bottomrule
\end{tabular}
\end{table}

### 2021-10-26 documents/sections/proto_carib.tex
various revisions
removed 'sleep' cognates

\begin{table}
	\centering
	\caption{\PC \setone (main clause) person markers \parencites[495]{meira2010origin}[497]{gildea2016referential}}
	\label{tab:pcpers}
\begin{subtable}[b]{.49\linewidth}
\caption{Transitive}
\label{tab:pctrans}
\centering
	\begin{tabular}{@{}lllll@{}}
	\mytoprule
\gl{a}/\gl{p}&		\gl{1}	&	\gl{2}		&	\gl{1+2}	&	\gl{3}	\\
\mymidrule
\gl{1}	&		&	\rc{k-}	&				&	\rc{t(i)-}		\\	
\gl{2}	&	\rc{k-}			&&				&	\rc{m(i)-}		\\
\gl{1+2}&		&				&				&	\rc{kɨt(i)-}		\\
\gl{3}	&	\rc{u(j)-}	&	\rc{ə(j)-}	&	\rc{k-}			&	\rc{n(i)-}		\\
	\mybottomrule
	\end{tabular}
\end{subtable}%
\begin{subtable}[b]{.49\linewidth}
\caption{Intransitive}
\label{tab:pcintrans}
\centering
\begin{tabular}{@{}lll@{}}
\mytoprule
& \gl{s_a_} & \gl{s_p_}  \\
\mymidrule
\gl{1} & \rc{w-} & \rc{u(j)-} \\
\gl{2} & \rc{m-} & \rc{ə(j)-}\\
\gl{1+2} & \rc{kɨt-} & \rc{k-}\\
\gl{3} & \rc{n-} & \rc{n(i)-}\\
\mybottomrule
\end{tabular}	
\end{subtable}
\end{table}

@@

\begin{table}
	\centering
	\caption{Underived \PC \gl{s_a_} verbs \parencite[30]{gildea2007greenberg}}
	\label{tab:underived2007}
	\begin{tabular}{@{}lll@{}}
	\mytoprule
Form & Meaning\\
\mymidrule
\rc{tə(mə)} & \qu{to go}\\
\rc{ətepɨ} & \qu{to come\subs{1}}\\
\rc{ka(ti)} & \qu{to say}\\
\rc{əmə(mɨ)} & \qu{to enter}\\
\rc{eti} & \qu{to dwell, be\subs{2}}\\
\rc{a(p)} & \qu{to be\subs{1}, say}\\
\rc{əməkɨ} & \qu{to come\subs{2}}\\
	\mybottomrule
	\end{tabular}
\end{table}

@@

\begin{table}[h]
\caption{Some examples for completed extensions \parencite[90--92]{gildea1998}}
\label{tab:completed}
\begin{subtable}[h]{0.24\textwidth}
\centering
\caption{\apalai}
\label{tab:apalai}
\begin{tabular}{@{}lll@{}}
\mytoprule
& \gl{s_a_} & \gl{s_p_}\\
\mymidrule
\gl{1} & ∅/\obj{ɨ-} & \obj{ɨ-}/\obj{j-}\\
\gl{2} & \obj{m(ɨ)-} & \obj{o-}\\
\gl{1+2} & \multicolumn{2}{c}{\emp{\obj{s(ɨ)-}}}\\
\gl{3} & \multicolumn{2}{c}{\obj{n(ɨ)-}}\\
\mybottomrule
\end{tabular}
\end{subtable}
\hfill
\begin{subtable}[h]{0.24\textwidth}
\centering
\caption{\panare}
\label{tab:panare}
\begin{tabular}{@{}lll@{}}
\mytoprule
& \gl{s_a_} & \gl{s_p_}\\
\mymidrule
\gl{1} & \obj{w(ɨ)-} & ∅/\obj{j-}\\
\gl{2} & \multicolumn{2}{c}{\emp{\obj{m(ɨ)-}}}\\
\gl{1+2} & \multicolumn{2}{c}{\obj{n(ɨ)-}}\\
\gl{3} & \multicolumn{2}{c}{\obj{n(ɨ)-}}\\
\mybottomrule
\end{tabular}
\end{subtable}
\hfill
%\begin{subtable}[h]{0.24\textwidth}
%\centering
%\caption{\pemon}
%\label{tab:pemon}
%\begin{tabular}{@{}lll@{}}
%\mytoprule
%& \gl{s_a_} & \gl{s_p_}\\
%\mymidrule
%\gl{1} & \multicolumn{2}{c}{\emp{∅}}\\
%\gl{2} & \multicolumn{2}{c}{\emp{\obj{m-}}}\\
%\gl{1+2} & \multicolumn{2}{c}{\obj{n-}}\\
%\gl{3} & \multicolumn{2}{c}{\obj{n-}}\\
%\mybottomrule
%\end{tabular}
%\end{subtable}
%\hfill
\begin{subtable}[h]{0.24\textwidth}
\centering
\caption{\waimiri}
\label{tab:waimiri}
\begin{tabular}{@{}ll@{}}
\mytoprule
& \gl{s}\\
\mymidrule
\gl{1} & \emp{\obj{w(ɨ)-}/\obj{i-}}\\
\gl{2} & \emp{\obj{m(ɨ)-}}\\
\gl{1+2} & \emp{\obj{h(ɨ)-}}\\
\gl{3} & \obj{n-}/∅\\
\mybottomrule
\end{tabular}
\end{subtable}
\end{table}

@@

%For instance, while the extension of \PWai \gl{1}\gl{s_p_} \rc{k-} affected most verbs, like \rc{eɸurka} \qu{to fall}, verbs like \rc{ka(ti)} \qu{to say} were not affected \exref{pwaiext}.

>>>>

\begin{table}
	\centering
	\caption[\PC \setone (main clause) person markers]{\PC \setone (main clause) person markers \parencites[495]{meira2010origin}[497]{gildea2016referential}}
	\label{tab:pcpers}
\begin{subtable}[b]{.49\linewidth}
\caption{Transitive}
\label{tab:pctrans}
\centering
	\begin{tabular}{@{}lllll@{}}
	\mytoprule
\gl{a}/\gl{p}&		\gl{1}	&	\gl{2}		&	\gl{1+2}	&	\gl{3}	\\
\mymidrule
\gl{1}	&		&	\rc{k-}	&				&	\rc{t(i)-}		\\	
\gl{2}	&	\rc{k-}			&&				&	\rc{m(i)-}		\\
\gl{1+2}&		&				&				&	\rc{kɨt(i)-}		\\
\gl{3}	&	\rc{u(j)-}	&	\rc{ə(j)-}	&	\rc{k-}			&	\rc{n(i)-}		\\
	\mybottomrule
	\end{tabular}
\end{subtable}%
\begin{subtable}[b]{.49\linewidth}
\caption{Intransitive}
\label{tab:pcintrans}
\centering
\begin{tabular}{@{}lll@{}}
\mytoprule
& \gl{s_a_} & \gl{s_p_}  \\
\mymidrule
\gl{1} & \rc{w-} & \rc{u(j)-} \\
\gl{2} & \rc{m-} & \rc{ə(j)-}\\
\gl{1+2} & \rc{kɨt-} & \rc{k-}\\
\gl{3} & \rc{n-} & \rc{n(i)-}\\
\mybottomrule
\end{tabular}	
\end{subtable}
\end{table}

@@

\begin{table}
	\centering
	\caption[Underived \PC \gl{s_a_} verbs]{Underived \PC \gl{s_a_} verbs \parencite[30]{gildea2007greenberg}}
	\label{tab:underived2007}
	\begin{tabular}{@{}lll@{}}
	\mytoprule
Form & Meaning\\
\mymidrule
\rc{tə[mə]} & \qu{to go}\\
\rc{ətepɨ} & \qu{to come\subs{1}}\\
\rc{ka[ti]} & \qu{to say}\\
\rc{əmə[mɨ]} & \qu{to enter}\\
\rc{eti} & \qu{to dwell, be\subs{2}}\\
\rc{a[p]} & \qu{to be\subs{1}, say}\\
\rc{əməkɨ} & \qu{to come\subs{2}}\\
	\mybottomrule
	\end{tabular}
\end{table}

@@

\begin{table}[h]
\caption[Some examples for completed extensions]{Some examples for completed extensions \parencite[90--92]{gildea1998}}
\label{tab:completed}
\begin{subtable}[h]{0.24\textwidth}
\centering
\caption{\apalai}
\label{tab:apalai}
\begin{tabular}{@{}lll@{}}
\mytoprule
& \gl{s_a_} & \gl{s_p_}\\
\mymidrule
\gl{1} & ∅/\obj{ɨ-} & \obj{ɨ-}/\obj{j-}\\
\gl{2} & \obj{m(ɨ)-} & \obj{o-}\\
\gl{1+2} & \multicolumn{2}{c}{\emp{\obj{s(ɨ)-}}}\\
\gl{3} & \multicolumn{2}{c}{\obj{n(ɨ)-}}\\
\mybottomrule
\end{tabular}
\end{subtable}
\hfill
\begin{subtable}[h]{0.24\textwidth}
\centering
\caption{\panare}
\label{tab:panare}
\begin{tabular}{@{}lll@{}}
\mytoprule
& \gl{s_a_} & \gl{s_p_}\\
\mymidrule
\gl{1} & \obj{w(ɨ)-} & ∅/\obj{j-}\\
\gl{2} & \multicolumn{2}{c}{\emp{\obj{m(ɨ)-}}}\\
\gl{1+2} & \multicolumn{2}{c}{\obj{n(ɨ)-}}\\
\gl{3} & \multicolumn{2}{c}{\obj{n(ɨ)-}}\\
\mybottomrule
\end{tabular}
\end{subtable}
\hfill
%\begin{subtable}[h]{0.24\textwidth}
%\centering
%\caption{\pemon}
%\label{tab:pemon}
%\begin{tabular}{@{}lll@{}}
%\mytoprule
%& \gl{s_a_} & \gl{s_p_}\\
%\mymidrule
%\gl{1} & \multicolumn{2}{c}{\emp{∅}}\\
%\gl{2} & \multicolumn{2}{c}{\emp{\obj{m-}}}\\
%\gl{1+2} & \multicolumn{2}{c}{\obj{n-}}\\
%\gl{3} & \multicolumn{2}{c}{\obj{n-}}\\
%\mybottomrule
%\end{tabular}
%\end{subtable}
%\hfill
\begin{subtable}[h]{0.24\textwidth}
\centering
\caption{\waimiri}
\label{tab:waimiri}
\begin{tabular}{@{}ll@{}}
\mytoprule
& \gl{s}\\
\mymidrule
\gl{1} & \emp{\obj{w(ɨ)-}/\obj{i-}}\\
\gl{2} & \emp{\obj{m(ɨ)-}}\\
\gl{1+2} & \emp{\obj{h(ɨ)-}}\\
\gl{3} & \obj{n-}/∅\\
\mybottomrule
\end{tabular}
\end{subtable}
\end{table}

@@

%For instance, while the extension of \PWai \gl{1}\gl{s_p_} \rc{k-} affected most verbs, like \rc{eɸurka} \qu{to fall}, verbs like \rc{ka[ti]} \qu{to say} were not affected \exref{pwaiext}.
